Optimal Decomposition-Recombination Plans for 2D Well-Constrained Graphs

### 2014-12-03 doc/GMP2015/s01_introduction.tex
s01_introduction.tex edited online with Bitbucket

\section{Introduction}
Computational design and analysis of constrained geometric configuration spaces of 2-dimensional, multilayered, aperiodic or self-similar materials and biological structures.

@@

Many natural and engineered materials are nearly rigid, 2D multilayers, possibly consisting of inter-constraining monolayers each of which is topologically planar (genus 0). They are often aperiodic, recursively self-similar or both \cite{Intro1}, enabling formation of diverse, larger structures with multiple functions.

@@

    \item interlinked monolayers of cellulose microfibrils e.g., in cell-walls \cite{CellWalls1} \cite{CellWalls1}

>>>>

\section{Introduction}
Constrained geometric configurations in layered materials and biological structures.

@@

Many natural and engineered materials are essentially two dimensional multilayers 
that not planar (genus 0). i.e., they consist of interconstraining planar monolayers. In addition,
they are often  
aperiodic and recursively self-similar \cite{Intro1}, enabling minimization of mass, 
optimal distribution of stresses, and formation  
of diverse, larger structures with multiple functions.

@@

    \item interlinked or interwoven cellulose or collagen microfibrils e.g., in cell-walls \cite{CellWalls1} \cite{CellWalls1}
